### 2021-07-13 src/paper/results/rapid_tests_statistics.tex
Shortened some parts of main text, added discussion of rapid tsts.

\begin{figure}[ht] % Share tested per day
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested}
        \caption{Share of the Population Doing a Rapid Test on a Given Day, by Channels}
        \label{fig:rapid_test_demand_by_channel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_positive}
        \caption{Share of the Population Testing Positive on a Given Day, by Channels}
        \label{fig:pos_rapid_tests_by_channel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_negative}
        \caption{Share of the Population Testing Negative on a Given Day, by Channels}
        \label{fig:neg_rapid_tests_by_channel}
    \end{subfigure}
    \caption{Rapid Test Shares in the Population by Channel}
    \floatfoot{\noindent \textit{Note:}
        Rapid tests in the education setting are demanded by teachers (nursery,
        preschool and school) as well as pupils. After Easter the required frequency of
        tests is increased from once per week to twice per week. Work rapid tests are
        demanded by individuals that still have work contacts, i.e. do not work from
        home. The share of employers offering rapid tests increases over the time frame
        and the frequency of testing is also increased. Private tests are demanded by
        individuals for one of three reasons: having developed symptoms without access
        to a PCR test, having a household member that has tested positive or developed
        symptoms or having planned a weekly meeting with friends. The left figure shows
        the share of the population doing a rapid test on a given day. The middle figure
        shows the share of the population testing positive on a given day (true and
        false positives). The right figure shows the share of the population testing
        negative on a given day (true and false negatives).}
\end{figure}

@@

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case, which can be seen from the
number of
false negative tests. At its peak at the beginning of May, there are more than 80 false
negative rapid tests per million inhabitants per day. While this number might sound low
in isolation, it becomes quite large when set in context: We estimate that at at the
the same time only 200 cases per million are detected by rapid tests. This means that
even at the time where discovery of cases via rapid tests is at its peak, almost
30\% of people who are infected and make a test are not discovered by the test.

>>>>

\begin{figure}[ht] % Share tested per day
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested}
        \caption{Share of the Population Doing a Rapid Test on a Given Day, by Channels}
        \label{fig:rapid_test_demand_by_channel}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/results/figures/rapid_test_statistics/popshare_tested_positive}
        \caption{Share of the Population Testing Positive on a Given Day, by Channels}
        \label{fig:pos_rapid_tests_by_channel}
    \end{subfigure}
    \caption{Rapid Test Shares in the Population by Channel}
    \floatfoot{\noindent \textit{Note:}
        Rapid tests in the education setting are demanded by teachers (nursery,
        preschool and school) as well as pupils. After Easter the required frequency of
        tests is increased from once per week to twice per week. Work rapid tests are
        demanded by individuals that still have work contacts, i.e. do not work from
        home. The share of employers offering rapid tests increases over the time frame
        and the frequency of testing is also increased. Private tests are demanded by
        individuals for one of three reasons: having developed symptoms without access
        to a PCR test, having a household member that has tested positive or developed
        symptoms or having planned a weekly meeting with friends.
        Panel~\subref{fig:rapid_test_demand_by_channel} shows the share of the
        population doing a rapid test on a given day.
        Panel~\subref{fig:pos_rapid_tests_by_channel} shows the share of the population
        testing positive on a given day (true and false positives).}
\end{figure}

@@

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case,\comment[id=HM]{I do not
understand. 80 fals neg for 200 true pos does not seem too reliable? I guess the
important bit is the reference cat. -- catching 200 pos vs. nothing} which can be seen
from the number of false negative tests. At its peak at the beginning of May, there are
more than 80 false negative rapid tests per million inhabitants per day. While this
number might sound low in isolation, it becomes quite large when set in context: We
estimate that at at the the same time only 200 cases per million are detected by rapid
tests. This means that even at the time where discovery of cases via rapid tests is at
its peak, almost 30\% of people who are infected and make a test are not discovered by
the test.
